Perceptions and Preferences for Meritocracy Scale (PPM-S)

### 2020-03-21 docs/preanalisis.Rmd
update21marzo

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

tab01 <- read.csv(file = "../input/data/original/materials/table01.csv",header = 1,sep = ";")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

@@

tab01 <- read.csv(file = "input/data/original/materials/table01.csv",header = 1,sep = ";")
